Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Typos

Directories contain lists of people with various information attached.
For instance, the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity, and by street name.
An typical example entry from this directory is "\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}".
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a description of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. }
    \label{fig.pipeline}
\end{figure}

>>>>

Directories contain lists of people with various information attached.
For instance, the directory published by \emph{Didot} in 1854 contains three redundant lists of people sorted by name, by activity and by street name.
A typical example entry from this directory is "\textit{Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.}".
It begins with the person's name and surname, here inside parentheses.
The glyph denotes that this person was awarded the \textit{Légion d'Honneur}.
Then comes a description of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. The
    NER Q.A. checkpoint may either assess the NER system lonely (the dashed
    \emph{groundtruth} path) or may evaluate the joint work of a NER
    system with an OCR system.}
    \label{fig.pipeline}
\end{figure}
